### 2025-04-08 correlation.qmd
20250408 - correlogram

```{r}
library("petersenlab")
library("XICOR")
library("psych")
library("DescTools")
library("tidyverse")
```

@@

>>>>

```{r}
library("petersenlab")
library("XICOR")
library("psych")
library("DescTools")
library("corrplot")
library("tidyverse")
```

@@

We can depict a correlogram using the `corrplot()` function of the `corrplot` package [@R-corrplot], as shown in @fig-correlogram.

```{r}
#| label: fig-correlogram
#| fig-cap: "Correlogram."
#| fig-alt: "Correlogram."

corrplot(cor(
  player_stats_seasonal[,c("height","weight","fantasyPoints")],
  use = "pairwise.complete.obs"))
```

### 2025-04-08 index.qmd
20250316 - package update
20250405 - updates
20250408 - correlogram

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nfl4th", "gsisdecoder", "progressr",
  "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", "ggdag",
  "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", "pROC",
  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", "AICcmodavg",
  "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", "viridis",
  "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", "stringi", #"webshot2", 
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin",
  "caret", "gpboost", "cmdstanr", "learnr", "remotes" #"mgcv",
)

knitr::write_bib(
  c(.packages(), packagesForBibliography),
  "packages_new.bib")
```

@@

>>>>

# Automatically create a bib database for R packages
packagesForBibliography <- c(
  "petersenlab", "ffanalytics",
  "knitr", "rmarkdown", "dplyr", "ggplot2", "tidyverse", "downlit", "xml2",
  "nflreadr", "nflplotR", "nflfastR", "nfl4th", "gsisdecoder", "progressr",
  "DescTools", "pwr", "pwrss", "WebPower", "XICOR", "dagitty", "ggdag",
  "lubridate", "ggtext", "gghighlight", "ggExtra", "grid", "patchwork", "pROC",
  "lme4", "lmerTest", "MuMIn", "emmeans", "pbkrtest", "sjstats", "AICcmodavg",
  "rstan", "brms", "bbmle", "fitdistrplus", "mclust", "magrittr", "viridis",
  "plotly", "quantmod", "fPortfolio", "xts", "zoo", "forecast", "stringi", #"webshot2", 
  "parallel", "parallelly", "doParallel", "missRanger", "ggridges", "powerjoin",
  "caret", "gpboost", "cmdstanr", "learnr", "remotes", "corrplot" #"mgcv",
)

xfun::pkg_bib(
  c(.packages(), packagesForBibliography),
  "packages_new.bib")
```

@@

<p>

You can also sponsor my open source work using <a href="https://github.com/sponsors/isaactpetersen">GitHub Sponsors</a>.
